systemfit: A Package to Estimate\\ Simultaneous Equation Systems in \proglang{R}

### 2006-08-29 paper/trunk/systemfit_restrictions.tex
rorganized the sections and subsections: there now a section called "Statistical Background" that includes the subsections (former sections) "Estimation", "Restrictions" and "Other issues" (a section of the "statistical background" is suggested by the JSS
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@614 591db2bd-e0a0-4d22-8c19-2192dbb7da31
corrected the paper according to all smaller comments of reviewer B except for the first point
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@684 591db2bd-e0a0-4d22-8c19-2192dbb7da31

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Imposing linear restrictions}\label{sec:Restrictions}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

There are two ways to impose linear parameter restrictions.
First, a matrix $T$ can be specified that
\begin{equation}
   \beta = T \cdot \beta^* \label{eq:T-restr} 
\end{equation}
where $\beta^*$ is a vector of restricted (linear independent) coefficients,
and $T$ is a matrix with the number of rows equal to the number of
unrestricted coefficients ($\beta$) and
the number of columns equal to the number of restricted coefficients
($\beta^*$).
$T$ can be used to map each unrestricted coefficient to one or more
restricted coefficients.

To impose these restrictions, the $X$ matrix is
(post-)multiplied by this $T$ matrix.
\begin{equation}
    X^* = X \cdot T
\end{equation}
Then, $X^*$ is substituted for $X$ and a standard estimation as described
in the previous section is done
(equations~\ref{eq:ols}--\ref{eq:3slsEViews}).
This results in the linear independent parameter estimates $\beta^*$ and
their covariance matrix.
The original parameters can be obtained by equation (\ref{eq:T-restr})
and the covariance matrix of the original parameters
can be obtained by:
\begin{equation}
   \Cov \left[ \widehat{\beta} \right] = T \cdot \Cov \left[ \widehat{\beta}^* \right] \cdot T'
\end{equation}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Restricted OLS estimation}
\label{sec:olsR}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Restricted WLS estimation}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Restricted SUR estimation}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Restricted 2SLS estimation}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Restricted W2SLS estimation}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Restricted 3SLS estimation}
\label{sec:3slsR}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Imposing linear restrictions}\label{sec:Restrictions}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

It is common to perform hypothesis tests by imposing restrictions on
the parameter estimates.
There are two ways to impose linear parameter restrictions.
First, a matrix $T$ can be specified that
\begin{equation}
   \beta = T \cdot \beta^* \label{eq:T-restr} 
\end{equation}
where $\beta^*$ is a vector of restricted (linear independent) coefficients,
and $T$ is a matrix with the number of rows equal to the number of
unrestricted coefficients ($\beta$) and
the number of columns equal to the number of restricted coefficients
($\beta^*$).
$T$ can be used to map each unrestricted coefficient to one or more
restricted coefficients.

To impose these restrictions, the $X$ matrix is
(post-)\hspace{0pt}multiplied by this $T$ matrix.
\begin{equation}
    X^* = X \cdot T
\end{equation}
Then, $X^*$ is substituted for $X$ and a standard estimation as described
in the previous section is done
(equations~\ref{eq:ols}--\ref{eq:3slsEViews}).
This results in the linear independent parameter estimates $\widehat{\beta}^*$ and
their covariance matrix.
The original parameters can be obtained by equation (\ref{eq:T-restr})
and the covariance matrix of the original parameters
can be obtained by:
\begin{equation}
   \Cov \left[ \widehat{\beta} \right] = T \cdot \Cov \left[ \widehat{\beta}^* \right] \cdot T'
\end{equation}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Restricted OLS estimation}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Restricted WLS estimation}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Restricted SUR estimation}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Restricted 2SLS estimation}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Restricted W2SLS estimation}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Restricted 3SLS estimation}
